### 2020-01-31 ChapterConclusion/chapterConclusion.tex
Updated: Rewrites and additions to Conclusion

An alternative to just aura position and radius being sent, more details of the object could be sent, including bounding sphere and velocity. This would allow the receiving server to determine the size of the aura. Under changing conditions, such as changes in latency the receiving server could dynamically change the size of the auras without the need for the sending server to send the new sizes of the auras.

Future experiments may also involve the decoupling of ``update rate'' from ``tick rate'' as described in Section \ref{update-rate-test-values}. As some video games opt to maintain a high internal tick rate to improve simulation accuracy but use a lower or variable update rate to save bandwidth when communicating with networked peers, it would be of interest to examine how doing so would affect the correctness of aura projection in these configurations.
Additionally, on-demand dynamic load balancing will be explored to enable improvements in scalability. This will leverage run-time resource (re)allocation in order to maintain efficient distribution of cloud-based processing facilities in response to changes in the simulated environment. Simulations of objects that can freely interact with one another with a high degree of fidelity are never uniform, and therefore on-line statistical modelling and analysis will be fundamental to predicting where additional computational units are required. This will necessitate a transition from fixed world region boundaries to dynamic re-partitioning, which we expect will improve performance by reducing the number of auras being projected and the number of objects being migrated, leading to an overall reduction in bandwidth usage.

@@

In order for the simulation to be truly scalable, new regions will need to be created during run-time (either dividing existing regions or expanding the simulation area). New nodes will need to be launched during run-time and a method for re-dividing up the workload between the new and existing nodes will be required.

>>>>

An alternative to just aura position and radius being sent over the network would be to send more details of the object projecting the aura. This could include bounding sphere and velocity and would allow the receiving server to determine the size of the aura. Under changing conditions, such as changes in latency the receiving server could dynamically change the size of the auras without the need for the sending server to send the new sizes of the auras.

The implementation of AP could be improved through the separation of the main server update rate and the network tick rate (network update frequency) as discussed in \ref{update-rate-test-values}. These two update rates are often decoupled in video games, as it enables the server to maintain an accurate simulation while allowing for a lower tick rate to reduce the network requirements i.e. bandwidth. A lower frequency tick rate would mean a larger aura is required as there would be a longer delay between aura creation/update/collisions events and messages being sent and a longer delay between a message being received and processed. Larger auras would likely lead to a drop in performance. However, a lower frequency tick rate would mean lower processing overhead for sending, receiving and processing network messages. This trade-off could be investigated to determine how it affects performance of the overall system.

%Future experiments may also involve the decoupling of ``update rate'' from ``tick rate'' as described in Section \ref{update-rate-test-values}. As some video games opt to maintain a high internal tick rate to improve simulation accuracy but use a lower or variable update rate to save bandwidth when communicating with networked peers, it would be of interest to examine how doing so would affect the correctness of aura projection in these configurations.

Scalability could be improved through the use of load-balancing and run-time elastic resources. Server regions could use dynamic boundaries to balance the workload of the simulation between servers. This could make use of existing research into graph-partitioning, where objects are treated as edges and overlapping auras are undirected edges. Boundaries could be moved to reduce the number of boundary-edge intersections. In addition, statistical modelling and analysis could be employed to predict future states of the simulation in order to reduce boundary-edge intersections that will occur. Through the use of elastic resources, it would also be possible to `spin-up' and `wind-down' nodes as required by the simulation. Combined with dynamic boundaries between servers, the simulation workload could be moved to newly created servers, by dividing existing server regions when computational requirements are high. When they are low, the regions from multiple servers could be consolidated into a single server, reducing the number of servers required, resulting in lower financial cost.

%, new regions will need to be created during run-time (either dividing existing regions or expanding the simulation area). New nodes will need to be launched during run-time, using  and a method for re-dividing up the workload between the new and existing nodes will be required. This would require on dem

%Additionally, on-demand dynamic load balancing will be explored to enable improvements in scalability. This will leverage run-time resource (re)allocation in order to maintain efficient distribution of cloud-based processing facilities in response to changes in the simulated environment. Simulations of objects that can freely interact with one another with a high degree of fidelity are never uniform, and therefore on-line statistical modelling and analysis will be fundamental to predicting where additional computational units are required. This will necessitate a transition from fixed world region boundaries to dynamic re-partitioning, which we expect will improve performance by reducing the number of auras being projected and the number of objects being migrated, leading to an overall reduction in bandwidth usage.

@@
